---
title: "APEC8003: Recitation 2"
author: 
  - "Shunkei Kakimoto" 
header-includes:
   - \usepackage{mathtools}
   - \usepackage{color}
   - \usepackage{amsmath}
output:
  xaringan::moon_reader:
    self_contained: true
    css: ../xaringan-themer.css 
    lib_dir: libs
    nature: 
      highlightStyle: github
      highlightLines: true
---
class: middle

```{r, child = '../setup.rmd', cache = FALSE}
```

```{r xaringan-scribble, echo=FALSE}
xaringanExtra::use_scribble()
```

```{r, include = F, cache = FALSE}
library(data.table)
library(ggplot2)
library(dplyr)
library(gganimate)
library(gifski)
library(gganimate)
# library(learnr)
```

```{r, include = F, eval=F, cache = FALSE}
httpgd::hgd()
httpgd::hgd_browse()
```

```{r xaringan-tachyons, echo=FALSE}
xaringanExtra::use_tachyons()
```

# Outline

1. Dominant strategy equilibrium and Iterated strict dominance (Lecture note 2, p 13 - 16) (10 mins)
2. Exercise problem 1 (20 mins)
3. Exercise problem 2 (20 mins)

???
+ This is the outline for today's session. 
+ In this week's assignment, There are questions related to Dominant strategy equilibrium and Iterated strict dominance, which we didn't cover in this week lectures'. So, I'm gonna explain about these concepts. 
+ And, I prepared some exercise problems, which might be helpful for this week's assignment. So, let's do it. 

---

# Quick Review

Last week, we leaned, 

Monopoly can capture more profit by 

+ Perfect price discrimination
+ Two-part tariffs 
+ Multi-market price discrimination

Oligopoly

+ Cournot (each firm chooses quantity)
+ Bertrand competition (each firm chooses price)
+ 

+ Cournot 

---

# Exercise Problem 1



???
+ Let's start with an easy question to 

