---
title: "APEC8003: Recitation 3"
author: 
  - "Shunkei Kakimoto" 
header-includes:
   - \usepackage{mathtools}
   - \usepackage{color}
   - \usepackage{amsmath}
output:
  xaringan::moon_reader:
    self_contained: true
    css: ../xaringan-themer.css 
    lib_dir: libs
    nature: 
      highlightStyle: github
      highlightLines: true
---
class: middle

```{r, child = '../setup.rmd', cache = FALSE}
```

```{r xaringan-scribble, echo=FALSE}
xaringanExtra::use_scribble()
```

```{r, include = F, cache = FALSE}
library(data.table)
library(ggplot2)
library(dplyr)
library(gganimate)
library(gifski)
library(gganimate)
# library(learnr)
```

```{r, include = F, eval=F, cache = FALSE}
httpgd::hgd()
httpgd::hgd_browse()
```

```{r xaringan-tachyons, echo=FALSE}
xaringanExtra::use_tachyons()
```

# Big picture

.content-box-green[**Assignment 1**]:
+ Romeo and Juliet, Battle of Sexes
+ Iterated strict dominance
  + If strategy A is dominated by strategy B for player 1, then there is no mixed strategy by player 2 that will make player 1 put any positive probability on playing B.
+ Public goods game

.content-box-green[**Assignment 2:**]
+ Monopolist, Two-part tariff
+ Edgeworth cycle
+ Cournot, Bertrand, and cartel outcome
+ Hotelling model of spatial competition
+ Strategic Commitment in Two-Stage Games
+ Infinitely repeated games: trigger strategy
+ Tariffs and imperfect international competition

???
+ Sometimes, stepping back and looking at the big picture of what we've learned so far can be helpful for you to improve your understanding.

+ This is a list of topics of the assignment problems that we have done. 
+ If you feel like you don't have **confidence in** some of these topics, I recommend that you go back and think about why you don't understand at first, and review the correspoding part in the lecture note, solve the problem again.  

---
class: middle

# Problem 3, Midterm Spring 2023

## Practice for Two-part tariff

The Mega-Meta Corporation is a monopolist in the production of game theory software. There are $N$ consumers of this software, $i = 1, 2, ..., N$. Each consumer $i$ has an inverse demand curve: $P_i (Q_i )=a-Q_i$, where $P_i$ is the price to consumer $i$, and $Q_i$ is quantity sold to consumer $i$. Assume there is a fixed cost, $F$, to develop the software, but no cost for distributing the software (zero marginal cost). The cost function for Mega-Meta is: $C(Q)=F$, where $Q=\sum_{i=1}^N Q_i$  (note: $C$ does not depend on $Q$ because marginal cost is zero). 

<b>a.</b> Suppose Mega-Meta chooses a quantity to sell to consumer $i$. What is the profit maximizing quantity to sell to consumer $i$. How much profit does Mega-Meta make over all $N$ consumers?
  
<b>b.</b> Now suppose that Mega-Meta charges a two-part tariff for each consumer: $T_i (Q_i )=x+yQ_i$, where $x$ is a fixed fee ("gate fee") and $y$ is a price per unit. What is the profit maximizing two-part tariff to charge each consumer? How much profit does Mega-Meta make over all $N$ consumers?

<br>

<div style="text-align: right"> (Continue to the next page) </div>

???
+ Okay, this is the problem that we gonna work on today. 
+ Last year, we had three problems on the midterm, and this problem was the final problem. I remembered that I got a bit confused in last part of this problem. I think this is a good problem to practice dynamic game, so let's do it. 
+ First, read the problem, and think about the first two questiones. 
  + The first question is easy, it's just asking about the monopoly profit. 
  + The second question is asking about Two-part tarrifs. 


---
class: middle 

# Problem 3, Midterm Spring 2023 (continue)

<b>c.</b> Finally suppose that Mega-Meta faces potential competition from Twenty-Cent Inc. Assume that Mega-Meta moves first and chooses a quantity to produce for each consumer $(Q_{i1})$. Next, Twenty-Cent decides whether or not to enter. If it enters, it pays a fixed cost of $F$, and then it chooses a quantity to sell to each consumer $(Q_{i2})$. If it doesn’t enter, then Twenty-Cent earns a $0$ payoff and Mega-Meta remains a monopolist. 

(i) Suppose that Mega-Meta anticipates entry and produces as a Stackelberg leader and Twenty-Cent plays as a Stackelberg follower. What is the Stackelberg equilibrium?

(ii) How much would Mega-Meta need to sell to each consumer in order to convince Twenty-Cent not to enter? 

(iii) Suppose that a = 12, N = 100 , and F = 400. What is the subgame perfect equilibrium in this case? 





